A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-07-08 tex/sec5-synthesis.tex
[ tex ] S5

\section{Bidirectional Type Synthesis and Checking} \label{sec:type-synthesis}
This section focuses on defining mode-correctness and deriving bidirectional type synthesis for any mode-correct bidirectional type system $(\Sigma, \Omega)$.
We start with presenting the statement of the decidability of bidirectional synthesis (whose proof will be deferred until \Cref{subsec:bidirectional-synthesis-checking}) and the trichotomy on raw terms in \Cref{subsec:trichotomy}.
We will combine mode preprocessing, soundness, and completeness from \Cref{sec:pre-synthesis} to exhibit the trichotomy as a corollary.
We will then formalise the mode-correctness condition and show the uniqueness of synthesized types in \Cref{sec:mode-correctness}.
This uniqueness property means that any two synthesised types for the same raw term $t$ under the same context $\Gamma$ have to be equal.
This will be used later in the proof of the decidability of bidirectional type synthesis and checking in \Cref{subsec:bidirectional-synthesis-checking}.

>>>>

\section{Bidirectional Type Synthesis and Checking} \label{sec:type-synthesis}
This section focuses on defining mode-correctness and deriving bidirectional type synthesis for any mode-correct bidirectional type system $(\Sigma, \Omega)$.
We start with the statement of the decidability of bidirectional synthesis and the trichotomy on raw terms for mode-correct bidirectional type systems in \Cref{subsec:trichotomy}, but defer the definition of mode-correctness until \Cref{sec:mode-correctness} and the decidability proof until \Cref{subsec:bidirectional-synthesis-checking}.
We will then formalise mode-correctness and show the uniqueness of synthesized types in \Cref{sec:mode-correctness}.
This uniqueness property means that any two synthesised types for the same raw term $t$ under the same context $\Gamma$ have to be equal.
This will be used later in the proof of the decidability of bidirectional type synthesis and checking in \Cref{subsec:bidirectional-synthesis-checking}.
